Dynein project log

### 2017-01-23 thesis/latex/thesis.tex
Fix k_ub parameter.

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{table:parameter-table}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{table:parameter-table}
\end{figure}

### 2017-01-23 thesis_stuff/thesis_stuff.tex
Add results of latest runs. Looks like unbinding probability still too high.
Fix k_ub parameter.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
\end{center}

@@

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | l | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & run & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & $3.7e-4$ & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & $4.6e-14$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & $5.4e-18$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
  \end{tabular}
  \textbf{New possibly right angle scheme run data}
\end{center}

@@

A more reliable step time determiner is $\Big<\mbox{step time}\Big>$, which should be around 0.1. This number can be determined from the step time histograms.\\

>>>>

%% \begin{center}
%%   \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
%%     \hline
%%     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
%%     $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
%%     $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
%%     $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
%%     $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
%%     $R_t$ &  & & & & 2.16nm & & & \\ \hline
%%     $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
%%     $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
%%     $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
%%     $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
%%     $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
%%     $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
%%     $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
%%     $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
%%     $c_t$ & & & & & & & & \\ \hline
%%     $c_m$ & & & & & & & & \\ \hline
%%     $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
%%   \end{tabular}
%% \end{center}

\textbf{Table moved to real elliott thesis!}

@@

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | l | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & run & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & $3.7e-4$ & & NaN! tail crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.25 & 2.25 & 2.25 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
    22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
  \end{tabular}
  \textbf{New possibly right angle scheme run data}
\end{center}

@@

A more reliable step time determiner is $\Big<\mbox{step time}\Big>$, which should be around 0.1. This number can be determined from our step time histograms.\\
